99-replications

### 2024-02-15 scripts/99-Replications.qmd
Final replications

---
title: "99-replications"
format: pdf
---
#### Preamble ####
# Purpose: Transform the raw data into csv format and clean out useless columns
# Author: Yichen Ji, Xiaoxu Liu
# Date: 13 February 2023
# Contact: yic.ji@mail.utoronto.ca, xiaoxu.liu@mail.utoronto.ca
# License: MIT
# Pre-requisites: Download tidyverse package
# Any other information needed? No.
## Quarto

@@

```{r lgbtq_rep, fig.width=4.7, fig.height=4}
#| echo: false
#| eval: true
#| warning: false

library(dplyr)
library(tidyr)
library(MetBrewer)

@@

data_long <- data_long %>%
  mutate(treatment = factor(treatment, levels = c("non-group-related control","control", "uncivil", "intolerant","threatening"), 
                            labels = c("No group mentioned", "Anti-target", "Uncivil post","Intolerant post","Threatening post")))

@@

ggplot(data_long, aes(x = fct_rev(treatment), y = percent, fill = handle)) +
  geom_bar(stat = "identity",width = 0.5) +
  theme_bw()+
  theme(
    legend.position = "bottom",
    legend.key.size = unit(0.3, "lines"),
    axis.title.y = element_text(face = "bold")
  ) +
  scale_fill_met_d(name = "Degas", direction = -1)+
   guides(
    fill = guide_legend(title = "How should social media \ncompanies handle the post?",
                        title.position = "left",
                        ncol = 3,# Position the title at the top
                        byrow = TRUE)  # Arrange items by row
  ) +
  labs(x = "", y = "Percent", fill = "") +
  coord_flip() +
  scale_y_continuous(expand = expansion(add = c(0, 0)))
```

```{r billion_rep, fig.width=4.7, fig.height=4}
#| echo: false
#| eval: true
#| warning: false

@@

ggplot(data_long, aes(x = fct_rev(treatment), y = percent, fill = handle)) +
  geom_bar(stat = "identity",width = 0.5) +
  theme_bw()+
  theme(
    legend.position = "bottom",
    legend.key.size = unit(0.3, "lines"),
    axis.title.y = element_text(face = "bold")
  ) +
  scale_fill_met_d(name = "Degas", direction = -1)+
   guides(
    fill = guide_legend(title = "How should social media \ncompanies handle the post?",
                        title.position = "left",
                        ncol = 3,# Position the title at the top
                        byrow = TRUE)  # Arrange items by row
  ) +
  labs(x = "", y = "Percent", fill = "") +
  coord_flip() +
  scale_y_continuous(expand = expansion(add = c(0, 0)))
```

```{r fig.width=12, fig.height=7.5}
#| echo: false
#| eval: true
#| warning: false

# Function to prepare data
prepare_data <- function(partisans, target_partisan) {
  partisans %>%
    filter(partisan == target_partisan | treatment == "non-group-related control") %>% 
    mutate(treatment = factor(treatment, 
                              levels = c("non-group-related control", "control", 
                                         "uncivil", "intolerant", "threatening"), 
                              labels = c("No group mentioned", "Anti-target", 
                                         "Uncivil post", "Intolerant post", "Threatening post"))) %>%
    count(treatment, handle) %>%
    pivot_wider(names_from = handle, values_from = n, values_fill = list(n = 0)) %>%
    mutate(total = rowSums(across(-treatment))) %>%
    mutate(across(-c(treatment, total), ~ .x / total * 100)) %>%
    pivot_longer(-c(treatment, total), names_to = "handle", values_to = "percent") %>%
    arrange(desc(treatment)) %>%
    mutate(handle = iconv(handle, from = "UTF-8", to = "ASCII", sub = "'")) # Convert non-ASCII characters to ASCII
}

# Function to generate plot with legend and bold title
generate_plot <- function(data_long, show_legend = FALSE) {
  p <- ggplot(data_long, aes(x = fct_rev(treatment), y = percent, fill = handle)) +
    geom_bar(stat = "identity", width = 0.5) +
    theme_bw() +
    theme(
      legend.position = "none",  # We will place the legend manually
      axis.title.x = element_text(size = 12),
      axis.text.y = element_text(face = "bold"),
      axis.text.x = element_text(size = 12),
      plot.margin = margin(5.5, 10, 5.5, 5.5)
    ) +
    scale_fill_met_d(name = "Degas", direction = -1) +
    labs(x = "", y = "Percent", fill = "") +
    coord_flip() +
    scale_y_continuous(expand = expansion(add = c(0, 0)))

  if (show_legend) {
    p <- p + theme(legend.position = "bottom") + 
      guides(
        fill = guide_legend(
          title = "How should social media companies \nhandle the post?",
          title.position = "left", 
          ncol = 3, 
          byrow = TRUE 
        )
      )
  }

@@

democrats_data_long <- prepare_data(iit_partisans_selected, "target: democrats")
republicans_data_long <- prepare_data(iit_partisans_selected, "target: republicans")

@@

# Combine plots and align the labels correctly
combined_plot <- plot_grid(
  democrats_plot + theme(plot.margin = margin(20, 10, 40, 5.5)), # Increase the top margin
  republicans_plot + theme(plot.margin = margin(20, 10, 40, 5.5)),
  labels = c("Target: Democrats", "Target: Republicans"),
  label_size = 12,
  label_fontface = "bold",
  hjust = -0.5, # Adjust horizontal position of labels
  vjust = 1.5,  # Adjust vertical position of labels
  ncol = 2
)

@@

# Print the final plot
print(final_plot)

>>>>

---
title: "99-replications"
format: pdf
#### Preamble ####
# Purpose: Transform the raw data into csv format and clean out useless columns
# Author: Yichen Ji, Xiaoxu Liu
# Date: 13 February 2023
# Contact: yic.ji@mail.utoronto.ca, xiaoxu.liu@mail.utoronto.ca
# License: MIT
# Pre-requisites: Download tidyverse package
# Any other information needed? Download all packages in the first chunck
---

@@

```{r, fig.width=5.5, fig.height=4}
#| echo: false
#| eval: true
#| label: fig-lgbtq-rep
#| fig-cap: Preferred actions in response to distinct post types - LGBTQ
#| warning: false

@@

data_long <- data_long %>%
  mutate(treatment = factor(treatment, levels = c("non-group-related","control", "uncivil", "intolerant","threatening"), 
                            labels = c("No group mentioned", "Anti-target", "Uncivil post","Intolerant post","Threatening post")))

@@

ggplot(data_long, aes(x = fct_rev(treatment), y = percent, fill = handle)) +
  geom_bar(stat = "identity", width = 0.5) +
  theme_bw() +
  theme(
    plot.margin = margin(10.5, 20.5, 20.5, 5.5),
    legend.position = c(0.35, -0.17), 
    legend.key.size = unit(0.4, "lines"), 
    legend.text = element_text(size = 5), 
    legend.title = element_text(size = 7), 
    axis.title.y = element_text(face = "bold")
  ) +
  scale_fill_met_d(name = "Degas", direction = -1) +
  guides(
    fill = guide_legend(
      title = "How should social media \ncompanies handle the post?",
      title.position = "left",
      ncol = 3,
      byrow = TRUE
    )
  ) +
  labs(x = "", y = "Percent", fill = "") +
  labs(title = "Target: LGBTQ") +
  theme(
    plot.title = element_text(hjust = -0.295, size = 9, face = "bold")
  )+
  coord_flip() +
  scale_y_continuous(expand = expansion(add = c(0, 0)))
```

```{r, fig.width=5.5, fig.height=4}
#| echo: false
#| eval: true
#| label: fig-billion-rep
#| fig-cap: Preferred actions in response to distinct post types - Billionaire
#| warning: false

@@

ggplot(data_long, aes(x = fct_rev(treatment), y = percent, fill = handle)) +
  geom_bar(stat = "identity", width = 0.5) +
  theme_bw() +
  theme(
    plot.margin = margin(10.5, 20.5, 20.5, 5.5),
    legend.position = c(0.35, -0.17), 
    legend.key.size = unit(0.4, "lines"), 
    legend.text = element_text(size = 5), 
    legend.title = element_text(size = 7), 
    axis.title.y = element_text(face = "bold")
  ) +
  scale_fill_met_d(name = "Degas", direction = -1) +
  guides(
    fill = guide_legend(
      title = "How should social media \ncompanies handle the post?",
      title.position = "left",
      ncol = 3,
      byrow = TRUE
    )
  ) +
  labs(x = "", y = "Percent", fill = "") +
  labs(title = "Target: Billionaires") +
  theme(
    plot.title = element_text(hjust = -0.24, size = 9, face = "bold")
  )+
  coord_flip() +
  scale_y_continuous(expand = expansion(add = c(0, 0)))
```

```{r fig.width=13, fig.height=7.8}
#| echo: false
#| eval: true
#| warning: false
partisans <- partisans %>%
  mutate(handle = gsub("Suspend the person’s account", "Suspend the person's account", handle))

# Function to prepare data
prepare_data <- function(partisans, target_partisan) {
  partisans %>%
    filter(partisan == target_partisan | treatment == "non-group-related control") %>% 
    mutate(treatment = factor(treatment, 
                              levels = c("non-group-related control", "control", 
                                         "uncivil", "intolerant", "threatening"), 
                              labels = c("No group mentioned", "Anti-target", 
                                         "Uncivil post", "Intolerant post", "Threatening post"))) %>%
    count(treatment, handle) %>%
    pivot_wider(names_from = handle, values_from = n, values_fill = list(n = 0)) %>%
    mutate(total = rowSums(across(-treatment))) %>%
    mutate(across(-c(treatment, total), ~ .x / total * 100)) %>%
    pivot_longer(-c(treatment, total), names_to = "handle", values_to = "percent") %>%
    arrange(desc(treatment))
}

# Function to generate plot with legend and bold title
generate_plot <- function(data_long, show_legend = FALSE) {
  p <- ggplot(data_long, aes(x = fct_rev(treatment), y = percent, fill = handle)) +
    geom_bar(stat = "identity", width = 0.5) +
    theme_bw() +
    theme(
      legend.position = "none",  # We will place the legend manually
      axis.title.x = element_text(size = 13.5),
      axis.text.y = element_text(size = 12),
      axis.text.x = element_text(size = 12),
      plot.margin = margin(5.5, 10, 5.5, 5.5)
    ) +
    scale_fill_met_d(name = "Degas", direction = -1) +
    labs(x = "", y = "Percent", fill = "") +
    coord_flip() +
    scale_y_continuous(expand = expansion(add = c(0, 0)))

  if (show_legend) {
    p <- p + theme(legend.position = c(0.49, 0.42)) + 
      guides(
        fill = guide_legend(
          title = "How should social media companies \nhandle the post?",
          title.position = "left", 
          ncol = 3, 
          byrow = TRUE 
        )
      )+
    theme(
      legend.title = element_text(size=14),
      legend.text = element_text(size=11.45),
      legend.key.size = unit(0.8, "lines"),
      legend.spacing.x = unit(0.4, "cm")
    )
 }

@@

democrats_data_long <- prepare_data(partisans, "target: democrats")
republicans_data_long <- prepare_data(partisans, "target: republicans")

@@

# Combine plots and align the labels correctly
combined_plot <- plot_grid(
  democrats_plot + theme(plot.margin = margin(60, 10, 20, 5.5)), # Increase the top margin
  republicans_plot + theme(plot.margin = margin(60, 10, 20, 5.5)),
  labels = c("Target: Democrats", "Target: Republicans"),
  label_size = 12,
  label_fontface = "bold",
  hjust = -0.59, # Adjust horizontal position of labels
  vjust = 6.7,  # Adjust vertical position of labels
  ncol = 2
)

@@

final_plot_with_title <- ggdraw() +
  draw_plot(final_plot) +
  draw_label("Preferred actions in response to distinct post types", 
             fontface = 'bold', 
             size = 14, 
             x = 0.5, 
             y = 0.98, 
             hjust = 0.5)

print(final_plot_with_title)
